---
title: "Results part 1"
author: "CCusack"
date: "10/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# data
```{r}
if (!require("tidyverse")) {install.packages("tidyverse"); require("tidyverse")}
if (!require("psych")) {install.packages("psych"); require("psych")}
if (!require("sjmisc")) {install.packages("sjmisc"); require("sjmisc")}

cbind.fill <- function(...){
    nm <- list(...) 
    nm <- lapply(nm, as.matrix)
    n <- max(sapply(nm, nrow)) 
    do.call(cbind, lapply(nm, function (x) 
        rbind(x, matrix(, n-nrow(x), ncol(x))))) 
}

cent = read.csv("cent_log.csv", header = TRUE, sep = ",", na.strings = "NA", stringsAsFactors = TRUE)
# ema data
groupdata = read.csv("ema_groupdata.csv", header = TRUE, sep = ",", na.strings = "NA", stringsAsFactors = TRUE)
DMS_baseline <- read.csv("DMS baseline clean.csv", na = "-99")
head(DMS_baseline)

setdiff(DMS_baseline$id_number, groupdata$ID) 

DMS_baseline <- DMS_baseline[-c(which(DMS_baseline$id_number=="DMS061"), which(DMS_baseline$id_number=="DMS064"), which(DMS_baseline$id_number=="DMS119")),] # n = 31

# followup
DMS_followup <- read.csv("DMS followup clean.csv", na = "-99")

DMS_followup <- DMS_followup[-c(which(DMS_followup$id_number=="DMS061"), which(DMS_followup$id_number=="DMS064")),]

# comorbidity data from screening interview
diagnosis <-readxl::read_xlsx("/Users/clairecusack/Dropbox/EAT LAB STUDIES (IN PROGRESS)/COMPLETED/Daily Mood Study (DMS)/Daily Mood Study/individual networks/TSIL 2021/data and code/dms_comorbidity.xlsx", na = "NA")
```

# Contemporaneous networks

```{r}
# frequency table of highest central symptom in descending order
table(cent$ContStrength_name1, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

meanssubset=cent[which(cent$NetType=="means"),]
table(meanssubset$ContStrength_name1, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

sdsubset=cent[which(cent$NetType=="variance"),]
table(sdsubset$ContStrength_name1, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

# see as proportion
prop.table(table(cent$ContStrength_name1, useNA = "ifany")) %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

# frequency table of the second highest central symptom in descending order
table(cent$ContStrength_name2, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))


# frequency table of the second highest central symptom in descending order
table(cent$ContStrength_name3, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

levels(cent$ContStrength_name1)
```

## means and var

In this chunk, I identify central symptoms for the contemporaneous networks including symptoms with the highest means and highest sds. 

```{r}
# frequency table of highest central symptom in descending order with nets consisting of sx with highest means
cent %>% 
  filter(NetType=="means") %>% 
  count(ContStrength_name1) %>% 
  arrange(desc(n))


# frequency table of highest central symptom in descending order with nets consisting of sx with highest variance
cent %>% 
  filter(NetType=="variance") %>% 
  count(ContStrength_name1) %>% 
  arrange(desc(n))
```

# Temporal networks

In this chunk, I determine which symptoms were most central in the temporal networks. Centrality was determined by OutStrength. To provide additional context for temporal networks, I also determine which symptoms were most frequently influenced by symptoms (e.g., highest InStrength). 

## outstrength
```{r}
# symptoms with the highest outstrength
table(cent$OutStrength_name1, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

prop.table(table(cent$OutStrength_name1, useNA = "ifany")) %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

table(meanssubset$OutStrength_name1, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

table(sdsubset$OutStrength_name1, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

# second highest centrality
table(cent$OutStrength_name2, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

# third highest centrality
table(cent$OutStrength_name3, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))
```

## instrength
```{r}
# symptoms with the highest instrength
table(cent$InStrength_name1, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

prop.table(table(cent$InStrength_name1, useNA = "ifany")) %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))


# symptoms with the second highest instrength
table(cent$InStrength_name2, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))

# symptoms with the second highest instrength
table(cent$InStrength_name3, useNA = "ifany") %>% 
        as.data.frame() %>% 
        arrange(desc(Freq))
```
## means and var

The most central sympt
```{r}
# most central sx in temporal networks consisting of sx with highest means
cent %>% 
  filter(NetType=="means") %>% 
  count(OutStrength_name1) %>% 
  arrange(desc(n))


# most central sx in temporal networks consisting of sx with highest sds
cent %>% 
  filter(NetType=="variance") %>% 
  count(OutStrength_name1) %>% 
  arrange(desc(n))

# symptoms with the highest instrength-means networks
cent %>% 
  filter(NetType=="means") %>% 
  count(InStrength_name1) %>% 
  arrange(desc(n))

# symptoms with the highest instrength-variance networks
cent %>% 
  filter(NetType=="variance") %>% 
  count(InStrength_name1) %>% 
  arrange(desc(n))
```

# unique symptom centrality
## overall
```{r}
# pull list of unique symptoms most central from contemporaneous networks and temporal networks
contemp_cent <- cent %>% select(ContStrength_name1) %>% as.list(unique()) %>% unlist()
temp_cent <- cent %>% select(OutStrength_name1) %>% as.list(unique()) %>% unlist()

intersect(contemp_cent, temp_cent)  # 20 the same
# "concentrate"     "difficultforget" "suppressemo"     "energy"          "bodydissat"     
# "restricturge"    "exerciseurge"    "weighurge"       "feargain"        "sad"            
# "feelfat"         "shortcomings"    "guilty"          "purgeurge"       "traumamem"      
# "dislikeself"     "sleep"           "workjob"         "anxiety"         "pleasure"  
setdiff(contemp_cent, temp_cent) # 10 in contemp, not in temporal 
# "cry"          "alwaysworry"  "diet"         "calcounturge" "criticalself" "irritable"   "worthless"    "restless"     "wsconc"       "desirethin"  
setdiff(temp_cent, contemp_cent) # 3 in temporal, 
# "overeat"   "decisions" "pastevent"
# 33 unique symptoms
```

## means and var
```{r}
# contemporaneous networks
contemp_cent_means <- cent %>% filter(NetType=="means") %>% select(ContStrength_name1) %>% as.list(unique()) %>% unlist()
contemp_cent_sds <- cent %>% filter(NetType=="variance") %>% select(ContStrength_name1) %>% as.list(unique()) %>% unlist()
intersect(contemp_cent_means, contemp_cent_sds)  # 6 the same
# "alwaysworry"  "restricturge" "criticalself" "bodydissat"   "feelfat"      "sad"    
setdiff(contemp_cent_means, contemp_cent_sds) # 10 in means, not in sds
# "concentrate"  "energy"       "calcounturge" "feargain"     "guilty"       "worthless"   
# "sleep"        "workjob"      "wsconc"       "anxiety"    
setdiff(contemp_cent_sds, contemp_cent_means) # 14 in sds, not in means
# "cry"             "difficultforget" "suppressemo"     "diet"            "exerciseurge"   
#  "weighurge"       "irritable"       "shortcomings"    "purgeurge"       "traumamem"      
#  "restless"        "dislikeself"     "desirethin"      "pleasure"   

# temporal networks
temp_cent_means <- cent %>% filter(NetType=="means") %>% select(OutStrength_name1) %>% as.list(unique()) %>% unlist()
temp_cent_sds <- cent %>% filter(NetType=="variance") %>% select(OutStrength_name1) %>% as.list(unique()) %>% unlist()
intersect(temp_cent_means, temp_cent_sds)  # 4 the same
# "difficultforget" "energy"          "purgeurge"      "weighurge"    
setdiff(temp_cent_means, temp_cent_sds) # 9 in means, not in sds
# "concentrate"  "feelfat"      "decisions"    "feargain"     "bodydissat"   "restricturge"
# "workjob"      "dislikeself"  "anxiety"     
setdiff(temp_cent_sds, temp_cent_means) # 10 in sds, not in means.
# "traumamem"    "overeat"      "sad"          "exerciseurge" "pleasure"     "shortcomings"
# "suppressemo"  "sleep"        "guilty"       "pastevent"  
```

# Which nets have temporal associations

I'm seeing which participants have temporal networks for means and variance
```{r}
cent %>% drop_na(OutStrength_name1) 

meansandvar <- cent %>% 
  pivot_wider(id_cols = ID, names_from = NetType, values_from = c(OutStrength_name1:ContStrength_value3), names_sep = ".") %>% 
  filter(!is.na(OutStrength_name1.means)& !is.na(OutStrength_name1.variance))

meansandvar$ID

rm(meansandvar)
```

# demos
```{r}
# gender
table(DMS_baseline$gender, useNA = "ifany")
DMS_baseline$gender <- as.factor(DMS_baseline$gender)
str(DMS_baseline$gender) # as factor
levels(DMS_baseline$gender) # check.
DMS_baseline$gender<- dplyr::recode(DMS_baseline$gender, "0" = "cis woman", "3" = "trans man", "4" = "nonbinary")
levels(DMS_baseline$gender)
table(DMS_baseline$gender, useNA = "ifany") 
prop.table(table(DMS_baseline$gender, useNA = "ifany") ) 

# ethnicity
table(DMS_baseline$ethnicity, useNA = "ifany")
DMS_baseline$ethnicity <- as.factor(DMS_baseline$ethnicity)
str(DMS_baseline$ethnicity) # as factor
levels(DMS_baseline$ethnicity) # check.

DMS_baseline$ethnicity<- dplyr::recode(DMS_baseline$ethnicity, "1" = "Asian or Pacific Islander", "2"= "Black", "3" = "Hispanic", "4" = "Bi/Multiracial", "5"="White")
levels(DMS_baseline$ethnicity)
table(DMS_baseline$ethnicity, useNA = "ifany") 
prop.table(table(DMS_baseline$ethnicity, useNA = "ifany") )

# age
describe(DMS_baseline$age) # mean = 25.55, sd = 8.63, median = 23, min = 18, max = 35
# edu
describe(DMS_baseline$yearsofschool) # mean = 15.06, sd = 2.56, min = 12, max = 22

str(DMS_baseline$work)
DMS_baseline$work <- as.factor(DMS_baseline$work)
table(DMS_baseline$work)

# diagnosis
## mood
diagnosis$MoodDisord <- rowSums(sapply(diagnosis[,c("MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp")], as.numeric), na.rm=TRUE)*NA^!rowSums(!is.na(diagnosis[,c("MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp")]))

diagnosis %>% filter(MoodDisord>0) # 28
diagnosis %>% filter(MDE>0) %>% tally() #17
diagnosis %>% filter(MDD>0) %>% tally() #11
diagnosis %>% filter(Bipolar_I>0) %>% tally() #2
diagnosis %>% filter(Bipoloar_II>0) %>% tally() #4
diagnosis %>% filter(HypomanicEp>0) %>% tally() #2

## anxiety
diagnosis$AnxietyDisord <- rowSums(sapply(diagnosis[,c("GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD")], as.numeric), na.rm=TRUE)*NA^!rowSums(!is.na(diagnosis[,c("GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD")]))

diagnosis %>% filter(AnxietyDisord>0) # 25
diagnosis %>% filter(GAD>0) %>% tally() #22
diagnosis %>% filter(SAD>0) %>% tally() #6
diagnosis %>% filter(SocialPhobia>0) %>% tally() #4
diagnosis %>% filter(SpecificPhobia>0) %>% tally() #2
diagnosis %>% filter(Agoraphobia>0) %>% tally() #9
diagnosis %>% filter(PTSD>0) %>% tally() #8
diagnosis %>% filter(`Panic Disorder`>0) %>% tally() #2
diagnosis %>% filter(LimitedSxPanic>0) %>% tally() #1
diagnosis %>% filter(OCD>0) %>% tally() #7

## eating disorder
diagnosis$ED <- rowSums(sapply(diagnosis[,c("AN-P", "AN-R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")], as.numeric), na.rm=TRUE)*NA^!rowSums(!is.na(diagnosis[,c("AN-P", "AN-R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")]))

diagnosis %>% filter(ED>0) # 20
diagnosis <- diagnosis %>% rename(AN_P="AN-P") %>% rename(AN_R="AN-R")

diagnosis %>% filter(AN_P>0) %>% tally() #7
diagnosis %>% filter(AN_R>0) %>% tally() #4
diagnosis %>% filter(AAN>0) %>% tally() #2
diagnosis %>% filter(BN>0) %>% tally() #6
diagnosis %>% filter(ABN>0) %>% tally() #1
diagnosis %>% filter(OSFED>0) %>% tally() #2
diagnosis %>% filter(BED>0) %>% tally() #1
diagnosis %>% filter(ABED>0) %>% tally() #1

diagnosis %>% filter(MoodDisord>0 &AnxietyDisord >0 & ED >0) # 17 had all 3
diagnosis %>% filter(MoodDisord==0 &AnxietyDisord >0 & ED ==0) # 0 # no one just had anxiety
diagnosis %>% filter(MoodDisord>0 &AnxietyDisord ==0 & ED ==0) # 2 just had mood
diagnosis %>% filter(MoodDisord==0 &AnxietyDisord ==0 & ED>0) # 2 just had ED
diagnosis %>% filter(MoodDisord>0 &AnxietyDisord ==0 & ED>0) # 1 just had ED and mood

```
# dx by participant for Figure 1

```{r}
# participant 1. DMS001
diagnosis %>% filter(ID=="DMS001") %>% select("MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 2. DMS005
diagnosis %>% filter(ID=="DMS005") %>% select("MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 3. DMS007
diagnosis %>% filter(ID=="DMS007") %>% select("MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 4. DMS008
diagnosis %>% filter(ID=="DMS008") %>% select("MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 5. DMS018
diagnosis %>% filter(ID=="DMS018") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 6. DMS022
diagnosis %>% filter(ID=="DMS022") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 7. DMS025
diagnosis %>% filter(ID=="DMS025") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 8. DMS027
diagnosis %>% filter(ID=="DMS027") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 9. DMS028
diagnosis %>% filter(ID=="DMS028") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 10. DMS035
diagnosis %>% filter(ID=="DMS035") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 11. DMS039
diagnosis %>% filter(ID=="DMS039") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 12. DMS053
diagnosis %>% filter(ID=="DMS053") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 13. DMS056
diagnosis %>% filter(ID=="DMS056") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 14. DMS062
diagnosis %>% filter(ID=="DMS062") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 15. DMS090
diagnosis %>% filter(ID=="DMS090") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 16. DMS092
diagnosis %>% filter(ID=="DMS092") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 17. DMS097
diagnosis %>% filter(ID=="DMS097") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 18. DMS098
diagnosis %>% filter(ID=="DMS098") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 19. DMS099
diagnosis %>% filter(ID=="DMS099") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 20. DMS100
diagnosis %>% filter(ID=="DMS100") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 21. DMS105
diagnosis %>% filter(ID=="DMS105") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 22. DMS107
diagnosis %>% filter(ID=="DMS107") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 23. DMS110
diagnosis %>% filter(ID=="DMS110") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 24. DMS111
diagnosis %>% filter(ID=="DMS111") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 25. DMS112
diagnosis %>% filter(ID=="DMS112") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 26. DMS113
diagnosis %>% filter(ID=="DMS113") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 27. DMS116
diagnosis %>% filter(ID=="DMS116") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 28. DMS123
diagnosis %>% filter(ID=="DMS123") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 29. DMS127
diagnosis %>% filter(ID=="DMS127") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 30. DMS130
diagnosis %>% filter(ID=="DMS130") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

# participant 31. DMS135
diagnosis %>% filter(ID=="DMS135") %>% select("MINI.Dx", "SCID.Dx", "MDE", "MDD", "Bipolar_I", "Bipoloar_II", "HypomanicEp", "GAD", "SAD", "SocialPhobia", "SpecificPhobia", "Agoraphobia", "PTSD", "Panic Disorder", "LimitedSxPanic", "OCD", "AN_P", "AN_R", "AAN", "BN", "ABN", "OSFED", "BED", "ABED")

```

```{r}
# DMS_baseline %>% filter(id_number=="DMS007") %>% select(bdi_clinical_totalscore) # 35
```

# depression remission

```{r}
# first see baseline
DMS_baseline %>% select(id_number, phq_1:phq_9)
# DMS027, DMS113 empty
setdiff(DMS_baseline$id_number, DMS_followup$id_number) 

DMS_baseline <- DMS_baseline %>%
  mutate(phq_baseline = rowSums(dplyr::select(., "phq_1":"phq_9"), na.rm = TRUE)* ifelse(rowSums(is.na(dplyr::select(., "phq_1":"phq_9"))) == ncol(dplyr::select(., starts_with("phq_"))), NA, 1))

DMS_baseline[which(DMS_baseline$phq_baseline == 0), which(colnames(DMS_baseline)=="phq_baseline")] <- NA

DMS_baseline %>% select(id_number, phq_1:phq_9, phq_baseline) # DMS027, DMS113 NA

# follow up
DMS_followup <- DMS_followup %>%
  mutate(phq_followup = rowSums(dplyr::select(., "phq_1":"phq_9"), na.rm = TRUE)* ifelse(rowSums(is.na(dplyr::select(., "phq_1":"phq_9"))) == ncol(dplyr::select(., starts_with("phq_"))), NA, 1))

DMS_followup[which(DMS_followup$phq_followup == 0), which(colnames(DMS_followup)=="phq_followup")] <- NA

DMS_followup %>% select(id_number, phq_1:phq_9, phq_followup) 

DMS_followup %>% select(id_number, starts_with("phq"))

DMS_followup_withphq <- as.data.frame(cbind.fill(DMS_followup, DMS_baseline$phq_baseline))
# remove extra rows (participants in baseline, not in follow up.)
DMS_followup_withphq <- DMS_followup_withphq[1:23,]
DMS_followup_withphq <- DMS_followup_withphq %>% rename(phq_baseline = V562)

DMS_followup_withphq %>% select(id_number, starts_with("phq"))

DMS_followup_withphq <-DMS_followup_withphq[-c(which(DMS_followup_withphq$id_number=="DMS027"), which(DMS_followup_withphq$id_number=="DMS028")),]

DMS_followup_withphq %>% select(id_number, starts_with("phq"))

DMS_followup_withphq$phq_baseline <- as.numeric(DMS_followup_withphq$phq_baseline)
DMS_followup_withphq$phq_followup <- as.numeric(DMS_followup_withphq$phq_followup)
# subtract follow up score from pre score
DMS_followup_withphq <- DMS_followup_withphq %>% mutate(phq_changescore = phq_baseline - phq_followup)
# see

DMS_followup_withphq[,c("id_number", "phq_baseline", "phq_followup", "phq_changescore")]

# percent change
DMS_followup_withphq$phq_percentchange <- ((DMS_followup_withphq$phq_followup-DMS_followup_withphq$phq_baseline)/DMS_followup_withphq$phq_baseline)*100
# check
DMS_followup_withphq[,c("id_number", "phq_baseline", "phq_followup", "phq_changescore", "phq_percentchange")]

DMS_followup_withphq <- DMS_followup_withphq %>% move_columns("phq_baseline", "phq_followup", "phq_changescore", "phq_percentchange", .after = phq_9)

# write.csv(DMS_followup_withphq, "DMS_followupwithphq.csv", row.names = FALSE)
```

```{r}
# file.choose()
prepost <- read.csv("/Users/clairecusack/Dropbox/EAT LAB STUDIES (IN PROGRESS)/COMPLETED/Daily Mood Study (DMS)/Daily Mood Study/group level project/data/prepostdata.csv", header = TRUE, sep = ",", stringsAsFactors = TRUE)
sum(is.na(prepost))/prod(dim(prepost)) # 0 
View(prepost)

prepost <- prepost[-c(which(prepost$ID=="DMS061"), which(prepost$ID=="DMS064"), which(prepost$ID=="DMS119")),] 


prepost$PHQ_total <- as.numeric(prepost$PHQ_total)
prepost$followup_PHQ_total <- as.numeric(prepost$followup_PHQ_total)
# subtract follow up score from pre score
prepost <- prepost %>% mutate(phq_changescore = PHQ_total - followup_PHQ_total)
# see

prepost[,c("ID", "PHQ_total", "followup_PHQ_total", "phq_changescore")]

# percent change
prepost$phq_percentchange <- ((prepost$followup_PHQ_total-prepost$PHQ_total)/prepost$PHQ_total)*100
# check
prepost[,c("ID", "PHQ_total", "followup_PHQ_total", "phq_changescore", "phq_percentchange")]

# write.csv(prepost, "DMS_prepostphq.csv", row.names = FALSE)
```

# alpha coef
## baseline bdi
```{r}
DMS_baseline[, which(grepl("bdi_([0-9]{1,2}_)clinical", colnames(DMS_baseline)))]

psych::alpha(DMS_baseline[, which(grepl("bdi_([0-9]{1,2}_)clinical", colnames(DMS_baseline)))])
# alpha = .86

psych::describe(prepost$BDI_clinical_total) # 33.94 sd 8.64
```

## phq-9 follow up
```{r}
DMS_followup[, which(grepl("^phq", colnames(DMS_followup)))]

psych::alpha(DMS_followup[, which(grepl("^phq", colnames(DMS_followup)))])
# alpha = .85
```
