---
title: "items_regularizednet"
author: "CCusack"
date: "2/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# set up 
```{r warning=FALSE, message=FALSE}
library(tidyverse)
source('./../../../individual networks/item_selfunction.R', encoding = 'UTF-8')
group_dat=read.csv("ema_groupdata_nonightlag.csv")
ids=unique(group_dat$ID)
rm(group_dat)

dat=data.frame(matrix(nrow = 62, ncol = 14))
names(dat)=c("id", "network", "symp1", "symp2", "symp3", "symp4", "symp5", "symp6", "symp1_cat", "symp2_cat", "symp3_cat", "symp4_cat", "symp5_cat", "symp6_cat")
dat[1]=rep(ids, each=2)
dat[2]=rep(c("means", "sd"))
```

# extract items 
```{r}
# set path
common_path = "/Users/clairecusack/Dropbox/EAT LAB STUDIES (IN PROGRESS)/COMPLETED/Daily Mood Study (DMS)/Daily Mood Study/individual networks"

# specify what I want
files_to_read = list.files(
  path = common_path,        # directory to search within
  pattern = "*_impute.csv$", # regex pattern, some explanation below
  recursive = TRUE,          # search subdirectories
  full.names = TRUE          # return the full path
)

# make list of participant dataframes
data_lst = lapply(files_to_read, read.csv)  # read all the matching files

# extract items and fill in df
for(i in 1:length(data_lst)){
 dat[which(dat$network=="means")[i],3:8]= unlist(matrix(unlist(item_sel(data.frame(data_lst[i]))), ncol=2, byrow = F)[,1])
 dat[which(dat$network=="sd")[i], 3:8]=unlist(matrix(unlist(item_sel(data.frame(data_lst[i]))), ncol=2, byrow = F)[,2])
}
```


# categorize items
```{r}
dep=c("energy", "sleep", "appetite", "decisions", "worthless", "cry", "guilty", "dislikeself","pleasure", "criticalself", "suppressemo", "concentrate", "irritable", "shortcomings", "sad", "failure")

anx=c("difficultforget", "traumamem", "anxiety", "nervoussocial", "worryoverwhelm", "interocept", "alwaysworry", "pastevent", "workjob", "restless", "controlthoughts")

ed=c("bodydissat", "overeat", "weighurge", "exerciseurge", "restricturge", "fasturge", "feelfat", "purgeurge", "feargain", "bingeurge", "calcounturge", "diet", "laxdiururge", "desirethin", "fasturge", "wsconc")


# fill out symptom type
for(i in dat[3:8]) {
  dat[,9] <- ifelse(dat$symp1 %in% dep, "dep", ifelse(dat$symp1 %in% anx, "anx", ifelse(dat$symp1 %in% ed, "ed", dat$symp1)))
  dat[10]=ifelse(dat$symp2 %in% dep, "dep", ifelse(dat$symp2 %in% anx, "anx", ifelse(dat$symp2 %in% ed, "ed", dat$symp2)))
  dat[11]=ifelse(dat$symp3 %in% dep, "dep", ifelse(dat$symp3 %in% anx, "anx", ifelse(dat$symp3 %in% ed, "ed", dat$symp3)))
  dat[12]=ifelse(dat$symp4 %in% dep, "dep", ifelse(dat$symp4 %in% anx, "anx", ifelse(dat$symp4 %in% ed, "ed", dat$symp4)))
  dat[13]=ifelse(dat$symp5 %in% dep, "dep", ifelse(dat$symp5 %in% anx, "anx", ifelse(dat$symp5 %in% ed, "ed", dat$symp5)))
  dat[14]=ifelse(dat$symp6 %in% dep, "dep", ifelse(dat$symp6 %in% anx, "anx", ifelse(dat$symp6 %in% ed, "ed", dat$symp6)))
}


# make factor
dat <- data.frame(lapply(dat, factor))
```

# frequency and percents
```{r}
dat %>% pivot_longer(everything(), values_drop_na = TRUE) %>% count(value) %>% arrange(desc(n)) 
# ed = 155, dep = 143, anx = 74

# apply((dat[9:14]), 2, table)
# sum(10,15,8,17,9,15) # 74 anx
# sum(22,17,26,20,28,30) # 143 dep
# sum(30,30,28,25,25,17) # 155 ed
prod(dim(dat[3:8])) # 372
(74/372)*100 # 19.89 anxious
(143/372)*100 # 38.44 dep
(155/372)*100 # 41.67 ed


# means nets
means=dat[which(dat$network=="means"),]
prod(dim(means[3:8])) # 186 # check
apply((means[9:14]), 2, table)
sum(4,6,3,8,3,9) # 33 anx
(sum(4,6,3,8,3,9)/186)*100 # 17.74% anxious

sum(12,10,11,10,13,11) # 67 dep
(sum(12,10,11,10,13,11)/186)*100 # 36.02% dep

sum(15,15,17,13,15,1) # 76 ed
(sum(15,15,17,13,15,1) /186)*100 # 40.86% ed

means %>% pivot_longer(everything(), values_drop_na = TRUE) %>% count(value) %>% arrange(desc(n)) 
# body dissat (n=20), feel fat (n=16), fear gain (n=14)


# sd nets
sd=dat[which(dat$network=="sd"),]
prod(dim(sd[3:8])) # 186
apply((sd[9:14]), 2, table)

sum(6,9,5,9,6,6) # 41 anx
(sum(6,9,5,9,6,6)/186)*100 # 22.04% anxious

sum(10,7,15,10,15,19) # 76 dep
(sum(10,7,15,10,15,19)/186)*100 # 40.86% dep

sum(15,15,11,12,10,6) # 69 ed
(sum(15,15,11,12,10,6)/186)*100 #37.10 ed

sd %>% pivot_longer(everything(), values_drop_na = TRUE) %>% count(value) %>% arrange(desc(n)) 
# energy (n=10), overeat (n = 10), weighurge (n = 9)
```

```{r}
dat %>% filter(network=="means") %>% select(symp1_cat:symp6_cat)
# dep anx ed:  14
# dep anx: 4
# dep ed:  6
# anx ed:  4
# ed: 1

dat %>% filter(network=="sd") %>% select(symp1_cat:symp6_cat)
# dep anx ed: 14
# dep anx: 6
# dep ed:  6
# anx ed:  5
# ed: 1
# dep: 

# total
# dep anx ed: 30
# dep anx: 10
# dep ed: 12
# anx ed: 5
# ed: 2
# dep 1
```

```{r}
dat %>% filter(network=="means") %>% pivot_longer(everything(), values_drop_na = TRUE) %>% count(value) %>% arrange(desc(n)) 

dat %>% filter(network=="sd") %>% pivot_longer(everything(), values_drop_na = TRUE) %>% count(value) %>% arrange(desc(n)) 
```

# means variability overlap

Seventeen participants had completely different symptoms in their means and standard deviation networks.

Six participants had one symptom included both, 

four participants had two symptoms in both, 

two participants had three symptoms in both, 

one participant had four symptoms in both, and one participant had 5 symptoms in both

```{r}
# View(dat)
# DMS001, DMS007, DMS025, DMS027, DMS039, DMS062, DMS090, DMS092, DMS097, DMS098, DMS099, DMS105, DMS110, DMS111, DMS112, DMS113, DMS116 no overlap (n = 17)
# DMS005 shares 2: traumamem and shortcomings
# DMS008 shares 4: sleep, appetite, bodydissat, energy
# DMS018 shares 2: sleep, purgeurge
# DMS022 shares 3: energy, sleep, alwaysworry
# DMS028 shares 2: concentrate, workjob
# DMS035 shares 1: weighurge
# DMS053 shares 1: sleep
# DMS056 shares 5: energy, sleep, fasturge, restricturge
# DMS100 shares 2: bodydissat, feelfat 
# DMS107 shares 1: sleep
# DMS123 shares 1: desirethin
# DMS127 shares 1: criticalself
# DMS130 shares 1: feelfat
# DMS135 shares 3: pleasure, energy, concentrate

# overlap
# ed: 9
# anx: 3
# dep : 16
```

# subset

How many combinations of symptoms are there not considering order
```{r}
datsymp_means = dat[which(dat$network=="means"),3:8]

data.frame(table(combo = sapply(split(as.matrix(datsymp_means), row(datsymp_means)), 
  function(x) paste(sort(x), collapse=" "))))
# each n = 1

datsymp_sd = dat[which(dat$network=="sd"),3:8]

data.frame(table(combo = sapply(split(as.matrix(datsymp_sd), row(datsymp_sd)), 
  function(x) paste(sort(x), collapse=" "))))
# each n = 1
```

## treemaps

### means
```{r}
datsymp_means = dat[which(dat$network=="means"),3:14]
occurences<-table(unlist(datsymp_means))
occurences
datsymp_means
#38
group <- c(rep("Anx",8),rep("MDD",17),rep("ED",12))
subgroup <- c("always worry","anxiety", "difficultforget", "interocept", "nervous social","trauma mem", "worry overwhelm","restless", # anx
                    "appetite", "cry", "decisions", "dislikeself","energy","guilty","pleasure","sleep", "worthless", "criticalself","suppress emo","workjob","concentrate", "irri- table", "short- comings", "failure","sad",#dep
                    "binge urge", "bodydissat","exercise urge", "fasturge", "feargain", "feelfat", "restrict urge", "weigh urge", "calcount urge", "diet", "desirethin", "wsconc")
value <- c(9, 12, 1, 2, 1, 1, 2, 2,
           12, 1, 5, 3, 12, 3, 3, 10, 3, 7, 1, 3, 3, 1, 1, 1, 1,
           1, 20, 2, 3, 14, 16, 8, 4, 4, 2, 6, 5)
means_tm <- data.frame(group,subgroup,value)

means_tm <-means_tm %>% 
  mutate(Symp.Index=paste(subgroup, value, sep ="\n"))

library(treemap)
png(filename="APSfigs/treemaps_means.png")
means_treemap=treemap(means_tm, index=c("group","Symp.Index"),     
        vSize="value", type="index",
        fontsize.labels=c(15,12),
        fontcolor.labels=c("white","black"),
        fontface.labels=c(2,1),                  # Font of labels: 1,2,3,4 for normal, bold, italic, bold-italic...
        bg.labels=c("transparent"),              # Background color of labels
        align.labels=list(
        c("left", "top"), 
        c("right", "bottom")
        ),                                   # Where to place labels in the rectangle?
    border.col=c("black","white"),
    overlap.labels=.5,                      # number between 0 and 1 that determines the tolerance of the overlap between labels. 0 means that labels of lower levels are not printed if higher level labels overlap, 1  means that labels are always printed. In-between values, for instance the default value .5, means that lower level labels are printed if other labels do not overlap with more than .5  times their area size.
    inflate.labels=F,                        # If true, labels are bigger when rectangle is bigger.
    title = "Frequency of Nodes Included in Mean Networks"
 
)
dev.off()
ggsave("APSfigs/treemaps_means.png", means_tm)
```
### sd
```{r}
datsymp_sd = dat[which(dat$network=="sd"),3:14]
occurences<-table(unlist(datsymp_sd))
occurences

#38
group <- c(rep("Anx",10),rep("MDD",17),rep("ED",15))
subgroup <- c("always worry","anxiety", "difficultforget", "interocept", "nervous social","trauma mem", "worry overwhelm","pastevent", "restless", "control thoughts", # anx
                    "appetite", "cry", "decisions", "dislikeself","energy","guilty","pleasure","sleep", "worthless", "criticalself","suppress emo","workjob","concentrate", "irri- table", "short- comings", "failure","sad",#dep
                    "binge urge", "bodydissat","exercise urge", "fasturge", "feargain", "feelfat", "overeat", "purge urge", "restrict urge", "weigh urge", "calcount urge", "diet", "lax diur urge", "desire thin", "wsconc")
value <- c(1, 3, 8, 3, 6, 5, 3, 7, 2,1,
           3, 8, 4, 5, 10, 5, 3, 8, 2, 6, 5, 2, 4, 3, 5, 3,2,
           7, 3,7, 7, 2, 2, 10, 8, 5, 9, 1, 2, 2, 3, 1)
sd_tm <- data.frame(group,subgroup,value)

sd_tm <-sd_tm %>% 
  mutate(Symp.Index=paste(subgroup, value, sep ="\n"))


treemap(sd_tm, index=c("group","Symp.Index"),     
        vSize="value", type="index",
        fontsize.labels=c(15,12),
        fontcolor.labels=c("white","black"),
        fontface.labels=c(2,1),                  # Font of labels: 1,2,3,4 for normal, bold, italic, bold-italic...
        bg.labels=c("transparent"),              # Background color of labels
        align.labels=list(
        c("left", "top"), 
        c("right", "bottom")
        ),                                   # Where to place labels in the rectangle?
    border.col=c("black","white"),
    overlap.labels=.5,                      # number between 0 and 1 that determines the tolerance of the overlap between labels. 0 means that labels of lower levels are not printed if higher level labels overlap, 1  means that labels are always printed. In-between values, for instance the default value .5, means that lower level labels are printed if other labels do not overlap with more than .5  times their area size.
    inflate.labels=F,                        # If true, labels are bigger when rectangle is bigger.
    title = "Frequency of Nodes Included in Variability Networks"
 
)
```

