---
title: "Btwn-Subjects Dataframe"
author: "CCusack"
date: "10/21/2021"
output: 
  html_document:
    toc: true
    toc_depth: 6
    toc_float: true
    number_sections: true
    code_folding: hide
    theme: cosmo
    df_print: paged
---

Working project title: From idiographic networks to between-subject prediction models of depressive outcomes.

Authors: Claire E. Cusack, M.A., Christina Ralph-Nearman, Ph.D., Caroline Christian, M.S., Aaron J. Fisher, Ph.D., & Cheri A. Levinson, Ph.D. (order tbd)    

The purpose of this markdown is to pull centrality metrics and node correlations from idiographic networks into a between subjects data frame. The idiographic networks were unreguarlized VAR networks. At the group level, the 6 symptoms with the highest means and highest standard deviations were identified.  

**top means:** body dissatisfaction, feeling fat, momentary anxiety, (lack of) energy, fear of weight gain, and always worry    
**top sds:** Fear of weight gain, feeling fat, desire to be thin, weight shape concentration, urge to restrict,  urge to diet

These symptoms were included in a means network and standard deviations were included in another network for each participant.

Columns include:    
- baseline and follow up depression scores    
- top 2 highest strength, in-strength, and out-strength values    
- edge weights from the contemporaneous and temporal networks for the means and standard deviation networks.    
- Conventions on column names: correlations from the means contemporaneous network are labeled _mc, means temporal labeled _mt, standard deviation contemporaneous _vc, standard deviation temporal _vt    

Rows are participants (*N* = 31).

We use data collected via EAT Lab's Daily Mood study, which was supported by Dr. Jesse H. Wright Endowment for Mood Disorders Research (funded 7/2019). Participants were adults experiencing a current depressive episode. We collected EMA data 4xday/20 days.

The aims of this project are exploratory.    

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      progress = FALSE)
```

# set up
```{r}
if (!require("tidyverse")) {install.packages("tidyverse"); require("tidyverse")}
if (!require("gdata")) {install.packages("gdata"); require("gdata")}

source('./../../item_selfunctiongroup.R', encoding = 'UTF-8')
names <- scan("./../../names.txt", what="character", sep = "\n")

# data
prepost <- read.csv("./../../Manuscript/Data and Code/DMS_prepostphq.csv")
ema <- read.csv("ema_groupdata_nonightlag.csv", na = "NA")
# head(ema)
# head(prepost)

# item_sel(ema[,8:49])
# top means: "bodydissat", "feelfat", "anxiety", "energy", "feargain", "alwaysworry"
# top sds: "feargain", "feelfat", "desirethin", "wsconc", "restricturge", "diet"

# create empty df
btwnsubdat <- data.frame(matrix(nrow = 31, ncol = 43))
# replace col names
colnames(btwnsubdat) <- names
btwnsubdat$ID <- unique(ema$ID) # fill in ID
rm(ema, item_sel) # don't need

# move over pre-post data to the between subjects df
btwnsubdat$Baseline_BDI <- prepost$BDI_clinical_total
btwnsubdat$Baseline_PHQ <- prepost$PHQ_total
btwnsubdat$Followup_PHQ <- prepost$followup_PHQ_total
btwnsubdat$PHQ_changescore <- prepost$phq_changescore
btwnsubdat$PHQ_percchange<- prepost$phq_percentchange
# for logistic regressions
btwnsubdat <- btwnsubdat %>%
  mutate(btwnsubdat, PHQ_nominal = 
         ifelse(PHQ_changescore <= -5, paste("Deterioration"),
         ifelse(PHQ_changescore >= 5, paste("Improvement"), paste("No change"))))
btwnsubdat$PHQ_nominal <- as.factor(btwnsubdat$PHQ_nominal) # make factor
table(btwnsubdat$PHQ_nominal) # 7 deterioration, 8 improvement, 16 no change
```

# network metrics
## DMS001
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS001/DMS001_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS001"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS001_centplotm, DMS001_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS005
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS005/DMS005_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS005"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS005_centplotm, DMS005_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS007
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS007/DMS007_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS007"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS007_centplotm, DMS007_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS008
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS008/DMS008_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS008"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS008_centplotm, DMS008_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS018
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS018/DMS018_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS018"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS018_centplotm, DMS018_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS022
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS022/DMS022_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS022"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS022_centplotm, DMS022_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS025
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS025/DMS025_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS025"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS025_centplotm, DMS025_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS027
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS027/DMS027_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS027"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS027_centplotm, DMS027_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS028
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS028/DMS028_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS028"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS028_centplotm, DMS028_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS035
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS035/DMS035_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS035"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS035_centplotm, DMS035_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS039
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS039/DMS039_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS039"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS039_centplotm, DMS039_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS053
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS053/DMS053_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS053"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS053_centplotm, DMS053_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS056
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS056/DMS056_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS056"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS056_centplotm, DMS056_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS062
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS062/DMS062_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS062"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS062_centplotm, DMS062_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS090
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS090/DMS090_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS090"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS090_centplotm, DMS090_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS092
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS092/DMS092_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS092"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS092_centplotm, DMS092_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS097
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS097/DMS097_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS097"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS097_centplotm, DMS097_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS098
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS098/DMS098_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS098"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS098_centplotm, DMS098_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS099
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS099/DMS099_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS099"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS099_centplotm, DMS099_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS100
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS100/DMS100_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS100"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS100_centplotm, DMS100_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS105
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS105/DMS105_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS105"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS105_centplotm, DMS105_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS107
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS107/DMS107_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS107"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS107_centplotm, DMS107_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS110
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS110/DMS110_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS110"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS110_centplotm, DMS110_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS111
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS111/DMS111_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS111"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS111_centplotm, DMS111_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS112
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS112/DMS112_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS112"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS112_centplotm, DMS112_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS113
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS113/DMS113_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS113"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS113_centplotm, DMS113_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS116
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS116/DMS116_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS116"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS116_centplotm, DMS116_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS123
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS123/DMS123_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS123"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS123_centplotm, DMS123_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS127
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS127/DMS127_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS127"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS127_centplotm, DMS127_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS130
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS130/DMS130_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS130"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS130_centplotm, DMS130_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

## DMS135
```{r}
# load .Rdata
load("./../../unregularized nets/group means sd nets/DMS135/DMS135_unreg.RData")
# pull strength means
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="Strength1_m"), which(colnames(btwnsubdat)=="Strength2_m"))] <- centr_m %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="In1_m"), which(colnames(btwnsubdat)=="In2_m"))] <- centr_m %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength means
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="Out1_m"), which(colnames(btwnsubdat)=="Out2_m"))] <- centr_m %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="Strength1_v"), which(colnames(btwnsubdat)=="Strength2_v"))] <- centr_sd %>% filter(measure=="Strength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull in-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="In1_v"), which(colnames(btwnsubdat)=="In2_v"))] <- centr_sd %>% filter(measure=="InStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# pull out-strength variance
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="Out1_v"), which(colnames(btwnsubdat)=="Out2_v"))] <- centr_sd %>% filter(measure=="OutStrength") %>% arrange(desc(value)) %>% top_n(2, value) %>% pull(value)

# strength cent means
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="BD_m"):which(colnames(btwnsubdat)=="AlwyWry_m"))]<-centr_m[1:6,5] # partial directed correlations

# strength cent sd
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="FearGain_sd"):which(colnames(btwnsubdat)=="Diet_sd"))]<-centr_sd[1:6,5] # partial directed correlations

# in out absolute value means
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="BD_inoutABS_m"):which(colnames(btwnsubdat)=="AlwyWry_inoutABS_m"))] <- abs(centr_m[7:12,5]) + abs(centr_m[13:18,5])

# in out absolute value sd
btwnsubdat[which(btwnsubdat$ID=="DMS135"), c(which(colnames(btwnsubdat)=="FearGain_inoutABS_sd"):which(colnames(btwnsubdat)=="Diet_inoutABS_sd"))] <- abs(centr_sd[7:12,5]) + abs(centr_sd[13:18,5])

# clean up env
rm(centr_m, centr_sd, data_means, data_sd, dedatm, dedatsd, DMS135_centplotm, DMS135_centplotsd, NetMean, NetSD, pcc_corr_m, pcc_corr_sd, pdc_m, pdc_sd, plot_grobm, plot_grobsd, beepvar, dayvar, i, vars_m, vars_sd, x, y, centralityPlot, gather_cent, kpss_df, kpss_plot, pcc_m, pcc_sd, pdc_corr_m, pdc_corr_sd, design.matrix)
```

# save
```{r}
# btwnsubdat
# name= 'btwnsubdat_cec'
# filetype= '.csv'
# filename= paste(name, Sys.Date(), filetype, sep='')
 
# write.csv(btwnsubdat,file=filename, row.names = FALSE)
# sessionInfo()
```


