---
title: "AJF 12272021"
author: "CCusack"
date: "12/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

predicting depression outcomes (PHQ 9 change score and clinical deterioration) at follow up.

Not enough data to split into training and test sets.

# packages and dat

```{r}
# clear work space
rm(list=ls())
# load("DMSmodels.RData") # bring in saved work

# packages
if (!require("tidyverse")) {install.packages("tidyverse"); require("tidyverse")} # can't not
if (!require("psych")) {install.packages("psych"); require("psych")} # descriptives and a lifeline
if (!require("glmnet")) {install.packages("glmnet"); require("glmnet")} # models
if (!require("pROC")) {install.packages("pROC"); require("pROC")} # AUC

# function for variable importance using cv.glmnet
source('varImp_fx.R', encoding = 'UTF-8')
# standardize coefficients. the standardized = TRUE argument doesn't work here
# if you relied on internal standardization by glmnet (default option standardize = TRUE), these standardized coefficients are actually the ones resulting from the fitting step, before retransformation by glmnet in the original space
# Normalized coeffcifient is the change in the result for a 1-standard-deviation change in the predictor

dat <- read.csv("./../preprocessing for predictive models/btwnsubdat_cec2021-12-27.csv", na = "NA")
head(dat)
# View(dat)
```
# EDA

Explore distribution of outcome vars and descriptive statistics
```{r}
hist(dat$PHQ_changescore) # normal
hist(dat$PHQ_percchange) # eh, more skewed but not worried about it

describe(dat)
# for means contemporaneous, cols 20:25
# for sd contemporaneous, cols 26:31
# for means temporal, cols 32:37
# for sd temporal, cols 38:43
```

# phq 9 change score 

## means
convention: objects are labeled "_mc" to indicate "means contemporaneous"

```{r}
# glmnet net needs it data in a matrix
mat_mc = as.matrix(dat[,c(which(colnames(dat)=="BD_m"):which(colnames(dat)=="AlwyWry_m"))]) # bd through always worry means
set.seed(10101)

# ridge regression
mod_mc = cv.glmnet(mat_mc, dat$PHQ_changescore, nfolds = 4, family = "gaussian", standardized = TRUE, alpha = 0) # default folds is 10
coef_mc = coef(mod_mc, s = "lambda.min") # ALwyWry_m = 0.28394520, BD_m = -0.15384249
coef_mc 
pred_mc = predict(mod_mc, newx=mat_mc, s="lambda.min")
cor.test(pred_mc, dat$PHQ_changescore)$estimate^2 # 0.1305552 == 13.06% variance
plot(mod_mc) 

# MSE
mse.min <- mod_mc$cvm[mod_mc$lambda == mod_mc$lambda.min] 
mse.min # 33.51151

# variable importance
varImp_cvglmnet(mat_mc, mod_mc)
stdcoefs_mc <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## sd
```{r}
mat_sd = as.matrix(dat[,c(which(colnames(dat)=="FearGain_sd"):which(colnames(dat)=="Diet_sd"))])
set.seed(10101)

# ridge regression
mod_sdc = cv.glmnet(mat_sd, dat$PHQ_changescore, nfolds = 4, family = "gaussian", standardized = TRUE, alpha = 0) # default folds is 10
coef_sdc = coef(mod_sdc, s = "lambda.min") 
coef_sdc 
# diet_sd = -0.17804920, FearGain_sd = -0.13290322, Restrict_sd = 0.13631865
pred_sdc = predict(mod_sdc, newx=mat_sd, s="lambda.min")
cor.test(pred_sdc, dat$PHQ_changescore)$estimate^2 # 0.1815858 == 18.16% variance

plot(mod_sdc) 
# MSE
mse.minsdc <- mod_sdc$cvm[mod_sdc$lambda == mod_sdc$lambda.min] 
mse.minsdc # 33.63717

# variable importance
varImp_cvglmnet(mat_sd, mod_sdc)
stdcoefs_sdc <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## means and sd
```{r}
mat_comb = as.matrix(dat[,c(which(colnames(dat)=="BD_m"):which(colnames(dat)=="Diet_sd"))])
set.seed(10101)

# ridge regression
mod_comb = cv.glmnet(mat_comb, dat$PHQ_changescore, nfolds = 4, family = "gaussian", standardized = TRUE, alpha = 0) # default folds is 10
coef_comb = coef(mod_comb, s = "lambda.min") 
coef_comb # AlwyWry_m = 0.30259429; Diet_sd = -0.24517734; Restrict_sd = 0.18535585, FearGain_sd = -0.17599341
pred_comb = predict(mod_comb, newx=mat_comb, s="lambda.min")
cor.test(pred_comb, dat$PHQ_changescore)$estimate^2 # 0.2815637 == 28.16% variance

plot(mod_comb) 
# MSE
mse.mincombc <- mod_comb$cvm[mod_comb$lambda == mod_comb$lambda.min] 
mse.mincombc # 33.44746

# variable importance
varImp_cvglmnet(mat_comb, mod_comb)
stdcoefs_combc <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## in and out str
### means
```{r}
mat_tempm = as.matrix(dat[,c(which(colnames(dat)=="BD_inoutABS_m"):which(colnames(dat)=="AlwyWry_inoutABS_m"))])
set.seed(10101)

# ridge regression
change_tempm = cv.glmnet(mat_tempm, dat$PHQ_changescore, nfolds = 4, family = "gaussian", standardized = TRUE, alpha = 0) # default folds is 10
coef_changetempm = coef(change_tempm, s = "lambda.min") 
coef_changetempm 
pred_changetempm = predict(change_tempm, newx=mat_tempm, s="lambda.min")
cor.test(pred_changetempm, dat$PHQ_changescore)$estimate^2 

plot(change_tempm) 
# MSe
mse.min_changetempm <- change_tempm$cvm[change_tempm$lambda == change_tempm$lambda.min] 
mse.min_changetempm # 33.67734

# variable importance
varImp_cvglmnet(mat_tempm, change_tempm)
stdcoefs_tempm <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

### sd
```{r}
mat_tempsd = as.matrix(dat[,c(which(colnames(dat)=="FearGain_inoutABS_sd"):which(colnames(dat)=="Diet_inoutABS_sd"))])
set.seed(10101)

# ridge regression
change_tempsd = cv.glmnet(mat_tempsd, dat$PHQ_changescore, nfolds = 4, family = "gaussian", standardized = TRUE, alpha = 0) # default folds is 10
coef_changetempsd = coef(change_tempsd, s = "lambda.min") 
coef_changetempsd 
pred_changetempsd = predict(change_tempsd, newx=mat_tempsd, s="lambda.min")
cor.test(pred_changetempsd, dat$PHQ_changescore)$estimate^2 

plot(change_tempsd) 
# MSE
mse.min_changetempsd <- change_tempsd$cvm[change_tempsd$lambda == change_tempsd$lambda.min] 
mse.min_changetempsd # 33.75268

# variable importance
varImp_cvglmnet(mat_tempsd, change_tempsd)
stdcoefs_tempsd <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

# binary outcome

phq 9 change score: Clinical deterioration, no change, or improvement

## means 
```{r}
# create dummy code vars
dat$improve = ifelse(dat$PHQ_nominal != "Improvement", 0, 1)
dat$deteriorate = ifelse(dat$PHQ_nominal != "Deterioration", 0, 1)
dat %>% select(PHQ_nominal, improve, deteriorate)

set.seed(1234)
deteriorate_m = cv.glmnet(mat_mc, dat$deteriorate, nfolds = 4, family = "binomial", standardized = TRUE, alpha = 0.0) 
coef_dm = coef(deteriorate_m, s = "lambda.min") # always worry = -0.101275435, feel fat = 0.045005412
coef_dm
pred_dm = predict(deteriorate_m, newx=mat_mc, s="lambda.min")
cor.test(pred_dm, dat$deteriorate)$estimate^2 # 0.1582932 # 15.93
pROC::auc(pROC::roc(dat$deteriorate~pred_dm)) # 0.756

pROC::coords((pROC::roc(dat$deteriorate~pred_dm)),"best", ret=c("threshold", "specificity", "sensitivity"), transpose=FALSE)
# threshold = -1.26, specificity = .5, sensitivity = 1

# variable importance
varImp_cvglmnet(mat_mc, deteriorate_m)
stdcoefs_deteriorm <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## sd 
```{r}
set.seed(1234)
deteriorate_sd = cv.glmnet(mat_sd, dat$deteriorate, nfolds = 4, family = "binomial", standardized = TRUE, alpha = 0.0) 
coef_dsd = coef(deteriorate_sd, s = "lambda.min") 
coef_dsd # tiny estimates
pred_dsd = predict(deteriorate_sd, newx=mat_sd, s="lambda.min")
cor.test(pred_dsd, dat$deteriorate)$estimate^2 # NA
pROC::auc(pROC::roc(dat$deteriorate~pred_dsd)) # .5 chance

# variable importance
varImp_cvglmnet(mat_sd, deteriorate_sd)
stdcoefs_deteriorsd <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## means and sd
```{r}
set.seed(1234)
deteriorate_comb = cv.glmnet(mat_comb, dat$deteriorate, nfolds = 4, family = "binomial", standardized = TRUE, alpha = 0.0) # default folds is 10

coef_dcomb = coef(deteriorate_comb, s = "lambda.min") 
coef_dcomb # tiny
pred_dcomb = predict(deteriorate_comb, newx=mat_comb, s="lambda.min")
cor.test(pred_dcomb, dat$deteriorate)$estimate^2 # 0.2060251 20.60%
pROC::auc(pROC::roc(dat$deteriorate~pred_dcomb)) # 0.8036

pROC::coords((pROC::roc(dat$deteriorate~pred_dcomb)),"best", ret=c("threshold", "specificity", "sensitivity"), transpose=FALSE)
# threshold = -1.23, specificity = 0.875, sensitivity =	0.7142857	

# variable importance
varImp_cvglmnet(mat_comb, deteriorate_comb)
stdcoefs_deteriorcomb <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## means temporal
```{r}
set.seed(1234)
deteriorate_tempm = cv.glmnet(mat_tempm, dat$deteriorate, nfolds = 4, family = "binomial", standardized = TRUE, alpha = 0.0) # default folds is 10

coef_dtempm = coef(deteriorate_tempm, s = "lambda.min") 
coef_dtempm # FearGain_inoutABS_m = 0.262133742, BD_inoutABS_m = -0.183181572, FeelFat_inoutABS_m = 0.168309441
pred_dtempm = predict(deteriorate_tempm, newx=mat_tempm, s="lambda.min")
cor.test(pred_dtempm, dat$deteriorate)$estimate^2 #0.1274739
pROC::auc(pROC::roc(dat$deteriorate~pred_dtempm)) # 0.7262

pROC::coords((pROC::roc(dat$deteriorate~pred_dtempm)),"best", ret=c("threshold", "specificity", "sensitivity"), transpose=FALSE)
# threshold = -1.388804, specificity = 0.4583333, sensitivity =	1	

# variable importance
varImp_cvglmnet(mat_tempm, deteriorate_tempm)
stdcoefs_deteriortempm <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## sd temporal
```{r}
set.seed(1234)
deteriorate_tempsd = cv.glmnet(mat_tempsd, dat$deteriorate, nfolds = 4, family = "binomial", standardized = TRUE, alpha = 0.0) # default folds is 10

coef_dtempsd = coef(deteriorate_tempsd, s = "lambda.min") 
coef_dtempsd# tiny estimates
pred_dtempsd = predict(deteriorate_tempsd, newx=mat_tempsd, s="lambda.min")
cor.test(pred_dtempsd, dat$deteriorate)$estimate^2 # NA
pROC::auc(pROC::roc(dat$deteriorate~pred_dtempsd)) # .5 chance

# variable importance
varImp_cvglmnet(mat_tempsd, deteriorate_tempsd)
stdcoefs_deteriortempsd <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```

## in and out temp
```{r}
mat_tempinout = as.matrix(dat[,c(which(colnames(dat)=="BD_inoutABS_m"):which(colnames(dat)=="AlwyWry_inoutABS_m"), which(colnames(dat)=="FearGain_inoutABS_sd"):which(colnames(dat)=="Diet_inoutABS_sd"))])

set.seed(10101)
deteriorate_inout = cv.glmnet(mat_tempinout, dat$deteriorate, nfolds = 4, family = "binomial", standardized = TRUE, alpha = 0.0) # default folds is 10

coef_dinout = coef(deteriorate_inout, s = "lambda.min") 
coef_dinout # tiny
pred_dinout = predict(deteriorate_inout, newx=mat_tempinout, s="lambda.min")
# cor.test(pred_dinout, dat$deteriorate)$estimate^2 
pROC::auc(pROC::roc(dat$deteriorate~pred_dinout)) # 0.50

pROC::coords((pROC::roc(dat$deteriorate~pred_dinout)),"best", ret=c("threshold", "specificity", "sensitivity"), transpose=FALSE)
# NA

# variable importance
varImp_cvglmnet(mat_comb, deteriorate_comb)
stdcoefs_deteriorcomb <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
deteriorate_inout = cv.glmnet(mat_comb, dat$deteriorate, nfolds = 4, family = "binomial", standardized = TRUE, alpha = 0.0) # default folds is 10

coef_dcomb = coef(deteriorate_comb, s = "lambda.min") 
coef_dcomb # tiny
pred_dcomb = predict(deteriorate_comb, newx=mat_comb, s="lambda.min")
cor.test(pred_dcomb, dat$deteriorate)$estimate^2 # 0.2060251 20.60%
pROC::auc(pROC::roc(dat$deteriorate~pred_dcomb)) # 0.8036

pROC::coords((pROC::roc(dat$deteriorate~pred_dcomb)),"best", ret=c("threshold", "specificity", "sensitivity"), transpose=FALSE)
# threshold = -1.23, specificity = 0.875, sensitivity =	0.7142857	

# variable importance
varImp_cvglmnet(mat_comb, deteriorate_comb)
stdcoefs_deteriorcomb <- std_coefs # rename df
rm(std_coefs) # remove auto saved df
```
