---
title: "DMS090 network code"
author: "CCusack"
date: "09/09/2021"
output: 
  html_document:
    toc: true
    toc_depth: 6
    toc_float: true
    number_sections: true
    code_folding: hide
    theme: cosmo
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      progress = FALSE)
```

# Set up

In this chunk I upload  necessary packages, functions, and data.

```{r warning=FALSE, message=FALSE}
# clear work space
rm(list=ls())

# packages
if (!require("tidyverse")) {install.packages("tidyverse"); require("tidyverse")}
if (!require("graphicalVAR")) {install.packages("graphicalVAR"); require("graphicalVAR")}
if (!require("qgraph")) {install.packages("qgraph"); require("qgraph")}
if (!require("tseries")) {install.packages("tseries"); require("tseries")}
if (!require("cowplot")) {install.packages("cowplot"); require("cowplot")} # figs
if (!require("grid")) {install.packages("grid"); require("grid")} # figs
if (!require("gridExtra")) {install.packages("gridExtra"); require("gridExtra")} # figs

# load funs
source('./../../centralityPlot source code facet y color change.R', encoding = 'UTF-8')
source('./../../kpss_dffunction.R', encoding = 'UTF-8')
source('./../../gather_centfunction.R', encoding = 'UTF-8')
source('./../kpss_plotfun.R', encoding = 'UTF-8')

# pull in imputed from earlier
data <- read.csv("./../../Manuscript/Data and Code/ema_groupdata_nonightlag.csv", na = "NA")
data <- data %>% filter(ID=="DMS090")
data_means <- data[, c("dayvar", "beepvar", "time", "lag", "tdif", "cumsumT", "bodydissat", "feelfat", "anxiety", "energy", "feargain", "alwaysworry")]
data_sd <- data[, c("dayvar", "beepvar", "time", "lag", "tdif", "cumsumT", "feargain", "feelfat", "desirethin", "wsconc", "restricturge", "diet")]

# check missingness. should be 0
sum(is.na(data[,-which(colnames(data)=="lag")]))/prod(dim(data[,-which(colnames(data)=="lag")])) # 0
```

# detrend means

This procedure is based off of Aaron Fisher et al. (2017) Exploring the idiographic dynamics of mood and anxiety via network analysis. https://osf.io/m63ks/ Instead of applying a cubic spline, the night lag was dropped.
```{r detrend means}
# trim
data_means =data_means[,7:12]
dedatm=data.frame(matrix(ncol = dim(data_means)[2], nrow = dim(data_means[1])))
colnames(dedatm)<-colnames(data_means)

# detrend
for(i in 1:ncol(dedatm)) {
  dedatm[,i] <- resid(lm(scale(data_means[,i])~data$cumsumT, na.action = na.exclude))
}

# add day and beep var back in
dedatm <- bind_cols(data[,2:3], dedatm)

vars_m = names(dedatm)[-c(1:2)] # create list of vars you want to check stationarity for
kpss_df(dedatm, vars_m)

x <- "beep" # make consec beep vector
y <- colnames(dedatm)[-c(1:2)] # make a vector from colnames not 1:6 ... everything else
design.matrix <- tidyr::expand_grid(x, y)

plot_grobm <- plot_grid(arrangeGrob(grobs=pmap(design.matrix, ~kpss_plot(x = .x, y = .y, df= dedatm))))
plot_grobm 
```

# detrend sd
```{r detrend sd}
# trim
data_sd =data_sd[,7:12]
dedatsd=data.frame(matrix(ncol = dim(data_sd)[2], nrow = dim(data_sd[1])))
colnames(dedatsd)<-colnames(data_sd)

# detrend
for(i in 1:ncol(dedatsd)) {
  dedatsd[,i] <- resid(lm(scale(data_sd[,i])~data$cumsumT, na.action = na.exclude))
}

# add day and beep var back in
dedatsd <- bind_cols(data[,2:3], dedatsd)

vars_sd = names(dedatsd)[-c(1:2)] # create list of vars you want to check stationarity
kpss_df(dedatsd, vars_sd)

x <- "beep" # make consec beep vector
y <- colnames(dedatsd)[-c(1:2)] # make a vector from colnames not 1:6 ... everything else
design.matrix <- tidyr::expand_grid(x, y)

plot_grobsd <- plot_grid(arrangeGrob(grobs=pmap(design.matrix, ~kpss_plot(x = .x, y = .y, df= dedatsd))))
plot_grobsd 
```


# networks

We estimate unregularized networks because we are pulling within-person results to use at between-subjects level. If we left graphicalVAR estimation results as default EBIC, each person would have different lambda values, which would render models uninterpretable when we zoom back out to group-level predictions.

## means results
```{r means net}
dayvar <- "dayvar"
beepvar <- "beepvar"

# estimate network
NetMean <- graphicalVAR(dedatm, vars=vars_m, dayvar=dayvar, beepvar=beepvar, gamma=0, lambda_beta = 0, lambda_kappa = 0, verbose = FALSE)

# save graphs separately to make it easier for formatting later.
pdf("DMS090_network_means_PCC.pdf", height=5, width=8)
pcc_m <- plot(NetMean, "PCC", labels= vars_m, edge.labels = TRUE, layout="spring")
dev.off()

pdf("DMS090_network_means_PDC.pdf", height=5, width=8)
pdc_m <- plot(NetMean, "PDC", labels = vars_m)
dev.off()

# create and save centrality plots
DMS090_centplotm <- plot(NetMean, labels= vars_m, edge.labels = TRUE, layout="spring") %>% 
  centralityPlot() +
  theme(legend.position = "none") +
  facet_grid(rows = vars(measure)) +
  theme(axis.text=element_text(size=13),
        strip.text.y = element_text(size=15))
ggsave(DMS090_centplotm, filename = "DMS090_centrality_m.png")

# centrality tables
centr_m<-gather_cent(pcc_m, pdc_m)
rm(centr)
write.csv(centr_m, "DMS090_centr_means.csv", row.names = FALSE)

# node correlations. Get edge list and weights
pcc_corr_m <- data.frame(pcc_m[[1]][[2]][[6]])
pcc_corr_m # look at it
write.csv(pcc_corr_m, "DMS090_pcc_corr_means.csv", row.names = TRUE)

pdc_corr_m <- data.frame(pdc_m[[1]][[2]][[5]])
pdc_corr_m # look at it
write.csv(pdc_corr_m, "DMS090_pdc_corr_means.csv", row.names = TRUE)
```

## variability results
```{r sd net}
dayvar <- "dayvar"
beepvar <- "beepvar"

# estimates network
NetSD <- graphicalVAR(dedatsd, vars=vars_sd, dayvar=dayvar, beepvar=beepvar, gamma=0, lambda_beta = 0, lambda_kappa = 0, verbose = FALSE)

# save graphs
pdf("DMS090_network_sd_PCC.pdf", height=5, width=8)
pcc_sd <- plot(NetSD, "PCC", labels= vars_sd, edge.labels = TRUE, layout="spring")
dev.off()

pdf("DMS090_network_sd_PDC.pdf", height=5, width=8)
pdc_sd <- plot(NetSD, "PDC", labels = vars_sd)
dev.off()

# create and save centrality plots
DMS090_centplotsd <- plot(NetSD, labels= vars_sd, edge.labels = TRUE, layout="spring") %>% 
  centralityPlot() +
  theme(legend.position = "none") +
  facet_grid(rows = vars(measure)) +
  theme(axis.text=element_text(size=13),
        strip.text.y = element_text(size=15))
ggsave(DMS090_centplotsd, filename = "DMS090_centrality_sd.png")

# centrality tables
centr_sd <- gather_cent(pcc_sd, pdc_sd)
rm(centr)
write.csv(centr_sd, "DMS090_centr_sd.csv", row.names = FALSE)

# node correlations
pcc_corr_sd <- data.frame(pcc_sd[[1]][[2]][[6]])
pcc_corr_sd # look at it
write.csv(pcc_corr_sd, "DMS090_pcc_corr_sd.csv", row.names = TRUE)

pdc_corr_sd <- data.frame(pdc_sd[[1]][[2]][[5]])
pdc_corr_sd # look at it
write.csv(pdc_corr_sd, "DMS090_pdc_corr_sd.csv", row.names = TRUE)
```
